Distributed Range-Only Localisation that Preserves Sensor and Navigator Privacies

### 2021-06-03 main.tex
Conclusion draft done

\section{Conclusion} \label{sec:conclusion}
To develop a Bayesian localization algorithm which preserves navigator and sensor privacy, we first defined the novel notion of an LCAO secure encryption scheme and gave a provably secure implementation based on the Paillier and Joye-Libert encryption and aggregation schemes, respectively. This scheme was then used in our proposed privacy-preserving EIF, where sensors compute measurement information homomorphically such that it can be privately used by a navigator. Our privacy-preserving estimation method may find uses in a variety of untrusted distributed localization environments including airspaces and autonomous vehicle networks as well as those where alternative measurement models satisfying our defined linearity requirements can be applied. Possible future work in this topic includes the expanding of the LCAO security notion to \textit{ensure} that the same weights are broadcast to all sensors, the application of LCAO secure schemes to alternative measurement models and the exploring of implications behind an active sensor attacker model.

@@

for some negligible functions $\eta_1$, $\eta_2$ and security parameter $\kappa$. That is, if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure (which is not the case \cite{joyeScalableSchemePrivacyPreserving2013}).

>>>>

\section{Conclusion} \label{sec:conclusion}
We have presented a localisation filter in the presence of range-only sensors, which preserves both navigator and sensor privacies. A suitable cryptographic scheme has been introduced and a filter implementation compared and evaluated. Privacy-preserving range-only localisation is suitable for use in environments where sensor networks are untrusted or location is considered private and we hope to extend the method to broader measurement models in the future. Additional future work includes exploring more computationally efficient encryption schemes and filter reformulations to increase the filter update frequency, exploring the possible security implications of sensors that are not only honest-but-curious and expanding the LCAO notion to guarantee that consistent broadcasts are always made by the navigator.

@@

for some negligible functions $\eta_1$, $\eta_2$ and security parameter $\kappa$. That is, if we assume our scheme is not LCAO secure, then the Joye-Libert scheme is not AO secure (which is not the case, \cite{joyeScalableSchemePrivacyPreserving2013}).
